Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-11-16 doc/Paper/main.tex
Couple of more changes.

    We expect mean galaxy properties to evolve as a function of redshift $z$ for the magnitude-limited sample considered in this analysis. Instead of fitting a separate HOD model to each redshift bin, we fit redshift-dependent functions to $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$ and choose a functional form given by:
    \begin{equation}
      \log{M_{i}(z)} = M_{i} + M_{i, p} \left(\frac{1}{1+z} - \frac{1}{1+z_{p}}\right),
    \end{equation}
    where $\log$ is the logarithm to base 10, $i \in [\mathrm{min}, 0, 1]$ and $z_{p}$ denotes a pivot redshift, which we set to $z_{p} = 0.65$. This functional form is motivated by an initial analysis in which we separately fit an HOD to each auto-power spectrum and determine a function consistent with the observed redshift evolution of the three parameters $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$. We additionally include a pivot redshift $z_{p}$ in our parametrization to remove degeneracies between the fitted parameters.

@@

  \subsection{Parameter constraints}\label{ssec:methods.constr}
    In order to derive constraints on HOD, cosmological and systematics parameters, we assume the joint likelihood of all auto- and cross-power spectra to be Gaussian 
    \begin{align}
      \mathscr{L}(D \vert \theta) = \frac{1}{[(2\pi)^{d}\det{\mathsf{C}}]^{\sfrac{1}{2}}} e^{-\frac{1}{2}(\mathbf{C}^{\mathrm{obs}}_{\ell}-\mathbf{C}^{\mathrm{theor}}_{\ell})^{\mathrm{T}}\mathsf{C}^{-1}(\mathbf{C}^{\mathrm{obs}}_{\ell}-\mathbf{C}^{\mathrm{theor}}_{\ell})}.
      \label{eq:likelihood}
    \end{align}
    The quantity $\mathsf{C}$ denotes the joint covariance matrix, which we estimate analytically as described in Sec.~\ref{sssec:methods.theory.covar} and which we keep constant during parameter estimation \citep{2019OJAp....2E...3K}.
    We sample the likelihood in a Monte Carlo Markov Chain (MCMC) using the publicly available code \texttt{CosmoHammer} \cite{Akeret:2013}, which is based on \texttt{emcee} \cite{Foreman-Mackey2013}\footnote{We note that we have compared the MCMC results obtained using \texttt{CosmoHammer} to those obtained using a Metropolis-Hastings algorithm as implemented in \texttt{april} (https://github.com/slosar/april), finding consistent results for our test case.}. In our fiducial analysis we sample the parameter set $\boldsymbol{\theta} = \{M_{\mathrm{min}}, \allowbreak \, M_{\mathrm{min}, p}, \allowbreak \, M_{0}, \allowbreak \, M_{0, p}, \allowbreak \, M_{1}, \allowbreak \, M_{1, p}, \allowbreak \, \Delta z_{i}, \allowbreak \, z_{w, i}\}$, $i = 0, \dots ,3$, where the first six parameters describe the HOD of galaxies as outlined in Sec.~\ref{sssec:methods.theory.hod}. The remaining parameters account for photometric redshift uncertainties as described in Sec.~\ref{sssec:methods.theory.photoz_syst}. We perform additional analyses in which we separately allow for variations in the amplitude $A_{\mu}$ of the magnification bias kernel $W_{\mu}$ and the cosmological parameters $\Omega_{c}$ and $\sigma_{8}$, where $\Omega_{c}$ is the fractional cold matter density today and $\sigma_{8}$ denotes the r.m.s. of linear matter fluctuations in spheres of comoving radius 8 $h^{-1}$ Mpc. For all sampled parameters, we assume flat, uniform priors. The sampled parameters are shown alongside their priors in Tab.~\ref{tab:params}. The remaining HOD parameters are set to $\alpha = 1.0$ and $\sigma_{\log M} = 0.4$. Unless stated otherwise, we further fix all cosmological parameters to the best-fit values derived by the Planck Collaboration in 2018 using temperature, polarization and CMB lensing data, i.e. $\Omega_{b}=0.0493$, $\Omega_{c}=0.264$, $h=0.6736$, $n_{s}=0.9649$ and $\sigma_{8}=0.8111$ (see the fourth column in Tab.~2 in \cite{Planck:2018}).

@@

    \begin{table*}
      \caption{Summary of parameters varied in the MCMC with their respective priors. The posterior means and best-fits are given for our fiducial analysis. The best-fit is defined as the maximum likelihood value of each parameter and the uncertainties denote the $68 \%$ c.l. corresponding to the equal-probability values encompassing a total probability of 0.68.} \label{tab:params}
      \begin{center}
        \begin{tabular}{cccc}
          \hline\hline 
          Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
          $M_{\mathrm{min}}$ & flat $\in [0., \,15.]$ & $11.88\substack{+0.22 \\ -0.23}$ & $12.02$ \\ 
          $M_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.491\substack{+2.09 \\ -2.02}$ & $-1.34$ \\
          $M_{0}$ & flat $\in [0., \,15.]$ & $5.72\substack{+3.95 \\ -3.97}$ & $6.60$ \\
          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.45\substack{+5.09 \\ -5.02}$ & $-1.43$ \\
          $M_{1}$ & flat $\in [0., \,17.]$ & $13.08\substack{+0.27 \\ -0.28}$ & $13.27$ \\ 
          $M_{1, p}$ & flat $\in [-12., \,15.]$ & $0.933\substack{+2.67 \\ -2.56}$ & $-0.323$ \\
          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.000339\substack{+0.096 \\ -0.091}$ & $-0.0642$ \\
          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $-0.0159\substack{+0.096 \\ -0.086}$ & $-0.0865$ \\
          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $-0.00588\substack{+0.105 \\ -0.094}$ & $-0.0681$ \\
          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0130\substack{+0.107 \\ -0.097}$ & $-0.0303$ \\
          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0451\substack{+0.123 \\ -0.113}$ & $-0.101$ \\
          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $-0.00962\substack{+0.0780 \\ -0.0789}$ & $-0.0103$ \\
          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0346\substack{+0.0789 \\ -0.0778}$ & $0.0824$ \\
          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0543\substack{+0.112 \\ -0.126}$ & $0.182$ \\ \\
          $A_{\mu}$ & flat $\in [-5., \,5.]$ & $ - $ & $ - $ \\
          $\Omega_{c}$ & flat $\in [0.1, \,0.9]$ & $ - $ & $ - $ \\
          $\sigma_{8}$ & flat $\in [0.2, \,1.5]$ & $ - $ & $ - $ \\
          \hline\hline 
        \end{tabular}
      \end{center}
    \end{table*}

@@

      Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $M_{\mathrm{min}}, \allowbreak \, M_{\mathrm{min}, p}, \allowbreak \, M_{1}, \allowbreak \, M_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}. The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}. As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.}. Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters alongside the measured power spectra. The corresponding minimum $\chi^{2}$ is $\chi^{2} = 86.2$. Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.08$ ($p$-value $= 0.30$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g. \cite{Andrae:2010}). However, we will use it throughout this work, as it allows us to obtain a rough estimate of the goodness of fit of the different models considered in our analysis.}.

@@

            Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       

@@

    The angular power spectrum is then given by
    \begin{equation}\label{eq:cell_gg_wmag}
      C^{ij}_\ell = \int \mathrm{d}z\,\frac{H(z)}{\chi^2(z)}\left[p^ip^j\,P_{gg}+\left(p^iW_\mu^j+p^jW_\mu^i\right)\frac{\ell(\ell+1)}{Hk^2}P_{gm}+W_\mu^iW_\mu^j\left(\frac{\ell(\ell+1)}{Hk^2}\right)^2P_{mm}\right],
    \end{equation}
    where $P_{mm}$ is the 3D power spectrum of matter fluctuations, $P_{gm}$ is the galaxy-matter cross-spectrum and we have omitted the dependence of all quantities on $z$ or $k=(\ell+1/2)/\chi$.

>>>>

    We expect mean galaxy properties to evolve as a function of redshift $z$ for the magnitude-limited sample considered in this analysis. Instead of fitting a separate HOD model to each redshift bin, we fit redshift-dependent functions to $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$ and choose a functional form given by:
    \begin{equation}
      \log{M_{i}(z)} = \mu_{i} + \mu_{i, p} \left(\frac{1}{1+z} - \frac{1}{1+z_{p}}\right),
    \end{equation}
    where $\log$ is the logarithm to base 10, $i \in [\mathrm{min}, 0, 1]$ and $z_{p}$ denotes a pivot redshift, which we set to $z_{p} = 0.65$. This functional form is motivated by an initial analysis in which we separately fit an HOD to each auto-power spectrum and determine a function consistent with the observed redshift evolution of the three parameters $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$. We additionally include a pivot redshift $z_{p}$ in our parametrization to remove degeneracies between the fitted parameters.

@@

  \subsection{Parameter constraints}\label{ssec:methods.constr}
    In order to derive constraints on HOD, cosmological and systematics parameters, we assume the joint likelihood of all auto- and cross-power spectra to be Gaussian 
    \begin{align}
      \mathscr{L}(D \vert \theta) = \frac{1}{[(2\pi)^{d}\det{\mathsf{C}}]^{\sfrac{1}{2}}} e^{-\frac{1}{2}(\mathbf{C}^{\mathrm{obs}}_{\ell}-\mathbf{C}^{\mathrm{theor}}_{\ell})^{\mathrm{T}}\mathsf{C}^{-1}(\mathbf{C}^{\mathrm{obs}}_{\ell}-\mathbf{C}^{\mathrm{theor}}_{\ell})}.
      \label{eq:likelihood}
    \end{align}
    The quantity $\mathsf{C}$ denotes the joint covariance matrix, which we estimate analytically as described in Sec.~\ref{sssec:methods.theory.covar} and which we keep constant during parameter estimation \citep{2019OJAp....2E...3K}.
    We sample the likelihood in a Monte Carlo Markov Chain (MCMC) using the publicly available code \texttt{CosmoHammer} \cite{Akeret:2013}, which is based on \texttt{emcee} \cite{Foreman-Mackey2013}\footnote{We note that we have compared the MCMC results obtained using \texttt{CosmoHammer} to those obtained using a Metropolis-Hastings algorithm as implemented in \texttt{april} (https://github.com/slosar/april), finding consistent results for our test case.}. In our fiducial analysis we sample the parameter set $\boldsymbol{\theta} = \{\mu_{\mathrm{min}}, \allowbreak \, \mu_{\mathrm{min}, p}, \allowbreak \, \mu_{0}, \allowbreak \, \mu_{0, p}, \allowbreak \, \mu_{1}, \allowbreak \, \mu_{1, p}, \allowbreak \, \Delta z_{i}, \allowbreak \, z_{w, i}\}$, $i = 0, \dots ,3$, where the first six parameters describe the HOD of galaxies as outlined in Sec.~\ref{sssec:methods.theory.hod}. The remaining parameters account for photometric redshift uncertainties as described in Sec.~\ref{sssec:methods.theory.photoz_syst}. We perform additional analyses in which we separately allow for variations in the amplitude $A_{\mu}$ of the magnification bias kernel $W_{\mu}$ and the cosmological parameters $\Omega_{c}$ and $\sigma_{8}$, where $\Omega_{c}$ is the fractional cold matter density today and $\sigma_{8}$ denotes the r.m.s. of linear matter fluctuations in spheres of comoving radius 8 $h^{-1}$ Mpc. For all sampled parameters, we assume flat, uniform priors. The sampled parameters are shown alongside their priors in Tab.~\ref{tab:params}. The remaining HOD parameters are set to $\alpha = 1.0$ and $\sigma_{\log M} = 0.4$. Unless stated otherwise, we further fix all cosmological parameters to the best-fit values derived by the Planck Collaboration in 2018 using temperature, polarization and CMB lensing data, i.e. $\Omega_{b}=0.0493$, $\Omega_{c}=0.264$, $h=0.6736$, $n_{s}=0.9649$ and $\sigma_{8}=0.8111$ (see the fourth column in Tab.~2 in \cite{Planck:2018}).

@@

    \begin{table*}
      \caption{Summary of parameters varied in the MCMC with their respective priors. The posterior means and best-fits are given for our fiducial analysis. The best-fit is defined as the maximum likelihood value of each parameter and the uncertainties denote the $68 \%$ c.l. corresponding to the equal-probability values encompassing a total probability of 0.68.} \label{tab:params}
      \begin{center}
        \begin{tabular}{cccc}
          \hline\hline 
          Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
          $\mu_{\mathrm{min}}$ & flat $\in [0., \,15.]$ & $11.88\substack{+0.22 \\ -0.23}$ & $12.02$ \\ 
          $\mu_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.491\substack{+2.09 \\ -2.02}$ & $-1.34$ \\
          $\mu_{0}$ & flat $\in [0., \,15.]$ & $5.72\substack{+3.95 \\ -3.97}$ & $6.60$ \\
          $\mu_{0, p}$ & flat $\in [-5., \,10.]$ & $2.45\substack{+5.09 \\ -5.02}$ & $-1.43$ \\
          $\mu_{1}$ & flat $\in [0., \,17.]$ & $13.08\substack{+0.27 \\ -0.28}$ & $13.27$ \\ 
          $\mu_{1, p}$ & flat $\in [-12., \,15.]$ & $0.933\substack{+2.67 \\ -2.56}$ & $-0.323$ \\
          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.000339\substack{+0.096 \\ -0.091}$ & $-0.0642$ \\
          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $-0.0159\substack{+0.096 \\ -0.086}$ & $-0.0865$ \\
          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $-0.00588\substack{+0.105 \\ -0.094}$ & $-0.0681$ \\
          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0130\substack{+0.107 \\ -0.097}$ & $-0.0303$ \\
          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0451\substack{+0.123 \\ -0.113}$ & $-0.101$ \\
          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $-0.00962\substack{+0.0780 \\ -0.0789}$ & $-0.0103$ \\
          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0346\substack{+0.0789 \\ -0.0778}$ & $0.0824$ \\
          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0543\substack{+0.112 \\ -0.126}$ & $0.182$ \\ \\
          $A_{\mu}$ & flat $\in [-5., \,5.]$ & $ - $ & $ - $ \\
          $\Omega_{c}$ & flat $\in [0.1, \,0.9]$ & $ - $ & $ - $ \\
          $\sigma_{8}$ & flat $\in [0.2, \,1.5]$ & $ - $ & $ - $ \\
          \hline\hline 
        \end{tabular}
      \end{center}
    \end{table*}

@@

      Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $\mu_{\mathrm{min}}, \allowbreak \, \mu_{\mathrm{min}, p}, \allowbreak \, \mu_{1}, \allowbreak \, \mu_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}. The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}. As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $\mu_{\mathrm{min}}, \, \mu_{\mathrm{min}, p}, \, \mu_{1}, \, \mu_{1, p}$.}. Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters alongside the measured power spectra. The corresponding minimum $\chi^{2}$ is $\chi^{2} = 86.2$. Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.08$ ($p$-value $= 0.30$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g. \cite{Andrae:2010}). However, we will use it throughout this work, as it allows us to obtain a rough estimate of the goodness of fit of the different models considered in our analysis.}.

@@

            Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $\mu_{\mathrm{min}, p}$ & $\mu_{\mathrm{min}}$ & $\mu_{1, p}$ & $\mu_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       

@@

    The angular power spectrum is then given by
    \begin{equation}\label{eq:cell_gg_wmag}
      C^{ij}_\ell = \int \mathrm{d}z\,\frac{H(z)}{\chi^2(z)}\left[p^ip^j\,P_{gg}+\left(p^iW_\mu^j+p^jW_\mu^i\right)\frac{\ell(\ell+1)}{Hk^2}P_{gm}+W_\mu^iW_\mu^j\left(\frac{\ell(\ell+1)}{Hk^2}\right)^2P_{mm}\right],
    \end{equation}
    where $P_{mm}$ is the 3D power spectrum of matter fluctuations, $P_{gm}$ is the galaxy-matter cross-spectrum and we have omitted the dependence of all quantities on $z$ or $k=\sfrac{(\ell+\sfrac{1}{2})}{\chi}$.
